Untrusted B2B Collaboration using the Blockchain

### 2018-07-19 paper/paper.tex
Add description of eth admin and armadillo

Thirdly, each organization uses \emph{access contracts} to manage which users can trigger events on the instance contracts.
Either, there is on access contract per process or access contracts are shared over multiple processes depending on the use case.

@@

\subsubsection{eth\_admin}

node-js command line tool using vorpal
commands trigger blockchain calls using web3

\subsubsection{armadillo}

>>>>

Thirdly, each organization uses \emph{access contracts} to manage which users can trigger events on the instance contracts.
Either there is one access contract per process or access contracts are shared over multiple processes depending on the use case.

@@

In the following, we will briefly present the tools we implemented integrate process management with our blockchain approach.
The implementations can be found in our repository at \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/}, in the \texttt{armadillo} and \texttt{eth\_admin} folders, respectively.
% TODO repo ist noch private
% TODO update if repository changes
% TODO overfull hbox

\subsubsection{Armadillo}

As a way of joining process execution with our blockchain architecture, we developed a single page web application in JavaScript and HTML, using the Vue.js framework\footnote{\url{https://vuejs.org}}.
With the help of the Web3 Ethereum JavaScript API\footnote{\label{web3}\url{https://github.com/ethereum/web3.js/}}, we can trigger contract functions based on user actions in the applications user interface.
Armadillo also implements the upload and rendering of BPMN diagrams using the bpmn.js toolkit\footnote{\url{https://bpmn.io/toolkit/bpmn-js/}}.
Building upon the BPMN viewer provided in the toolkit, we implemented the handling of user clicks on tasks, which allowed us to use the viewer as a process engine mock.
A screencast of the full choreography can be found in the respository under \url{https://github.com/p-otto/ProcessesMeetBlockchain2018/blob/master/presentation/armadillo-screencast.mp4}.
% TODO repo, hbox etc.

\subsubsection{Eth\_Admin}

We developed a small command line application for managing users and roles via the access contract.
The application is written in JavaScript in the node.js framework\footnote{\url{https://nodejs.org/}}.
Internally, calls functions on access contracts utilizing the Web3 Ethereum JavaScript API\textsuperscript{\ref{web3}}.
We decide to build the command line functionality with the help of the Vorpal framework\footnote{\url{http://vorpal.js.org/}}.
The README in our repository describes how to use the application.
